Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-29 paper/gd1.tex
mesa MIST refs

TODO: hints of density variations from initial work Koposov:2010, later confirmed by density modeling, but all low significance
(\citealt{Carlberg:2013}).
More recently, deep photometry of GD-1 from CFHT/Megacam has revealed
interesting small-scale ``wiggles'' and significant density variations along a $\approx 45^\citc$ span of the stream (\citealt{DeBoer:2017}):
[summarize their conclusions].

@@

To improve the contrast of the stream over the background, we next cross-match
the sample to the \pans\ photometric catalog and use the photometry to further
clean the sample.
\figurename~\ref{fig:selection} (bottom right) shows the distribution of
proper-motion-selected candidate stream stars in a de-reddened \pans\
color-magnitude diagram.
\todo{Did you also cut on $phi_2$?}.
The over-plotted isochrone is from the MESA Isochrones & Stellar Tracks (MIST;
\citealt{XX}) and represents a $12~\textrm{Gyr}$ old population with $\feh =
-1.XX$ at a distance of $XX~\kpc$.
We use this isochrone to motivate a polygonal selection in de-reddened $g-i$
color and apparent $g$-band magnitude, as visualized by the \todo{shaded} region
in the bottom right panel of \figurename~\ref{fig:selection}.

>>>>

\todo{hints of density variations} from initial work Koposov:2010, later confirmed by density modeling, but all low significance
(\citealt{Carlberg:2013}).
More recently, deep photometry of GD-1 from CFHT/Megacam has revealed
interesting small-scale ``wiggles'' and significant density variations along a $\approx 45^\citc$ span of the stream (\citealt{DeBoer:2017}):
[summarize their conclusions].

@@

To improve the contrast of the stream over the background, we next cross-match
the sample to the \pans\ photometric catalog and use the photometry to further
clean the sample.
\figurename~\ref{fig:selection} (bottom right) shows the distribution of
proper-motion-selected candidate stream stars in a de-reddened \pans\
color-magnitude diagram.
\todo{Did you also cut on $phi_2$?}.
The over-plotted isochrone is from the MESA Isochrones \& Stellar Tracks (MIST;
\citealt{Dotter:2016, Choi:2016, Paxton:2011}) and represents a
$12~\textrm{Gyr}$ old population with $\feh = -1.XX$ at a distance of $XX~\kpc$.
We use this isochrone to motivate a polygonal selection in de-reddened $g-i$
color and apparent $g$-band magnitude, as visualized by the \todo{shaded} region
in the bottom right panel of \figurename~\ref{fig:selection}.
